---
title: "Assignment4"
author: "Steve Jones"
date: "April 9, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#getwd()
#setwd("C:/Rockhurst/ADM/Data")

#Github local directory
setwd("C:/Rockhurst/ADM/Scripts/ADM_Week_4/data")

library(arules) 
bookbaskets <- read.transactions("bookdata.tsv.gz", format="single",  	# Note: 2 
                                 sep="\t",                    	# Note: 3 
                                 cols=c("userid", "title"),    	# Note: 4 
                                 rm.duplicates=T)       	# Note: 5

# Note 1: 
#   Load the arules package. 

# Note 2: 
#   Specify the file and the file format. 

# Note 3: 
#   Specify the column separator (a tab). 

# Note 4: 
#   Specify the column of transaction IDs and of 
#   item IDs, respectively. 

# Note 5: 
#   Tell the function to look for and remove 
#   duplicate entries (for example, multiple entries 
#   for “The Hobbit” by the same user). 

# 92,108 book purchases.
#220,447 user IDs.

inspect(bookbaskets[1:5]) #Examine the first five transactions

basketSizes<-size(bookbaskets) #Calculate number of books purchased by "userID"


bookFreq<-itemFrequency(bookbaskets) #Calculate the support for each book title 


bookCount <- (bookFreq/sum(bookFreq))*sum(basketSizes) 
#   Get the absolute count of book occurrences. 


bookbasket_use<-bookbaskets[basketSizes>1] #Only keep transactions with more than one book purchased. 

bookbasket_use
```
```{r}
#***********************************************************************************************
#Examine data set
dim(bookbasket_use)[1]
class(bookbasket_use)
colnames(bookbasket_use)
#***********************************************************************************************


Top10Books<-itemFrequencyPlot(bookbaskets, topN = 10) #top 10
#The Top 10 selling titles for Flourish abd Blotts bookstore are:
# 1. Wild Animus
# 2. The Lovely Bones: A Novel
# 3. She's Come Undone
# 4. The Da Vinci Code
# 5. Harry Potter and the Sorcerer's Stone
# 6. The Nanny Diaries: A Novel
# 7. A Painted House
# 8. Bridget Jones's Diary
# 9. The Secret Life of Bees
# 10.Divine Secrets of the Ya-Ya Sisterhood: A Novel


#*************************************************
```
#```{r}
# Select support and confidence
# Support = supported by at least 250 customers: 250/40822[1] = .006 <<< I'll start here and tweak based on trial run
# confidence = 75% 

#Let's try Support = 0.006. Confidence = 0.75.
# Bookbaskets_rules_250 <- apriori(bookbaskets, parameter = list(support = 0.006, confidence = 0.75)) 
# #Outcome = 0 rules
# ```
# ```{r}
# #Trying Support = 0.003. Confidence = 0.75.
# #Support = supported by at least 125 customers: 250/40822[1] = .003
# Bookbaskets_rules_125 <- apriori(bookbaskets, parameter = list(support = 0.003, confidence = 0.75)) 
# #Outcome = 0 rules
# ```
```{r}
#Trying Support = 0.001. Confidence = 0.75.
#Trying Support = 0.001. Confidence = 0.80.
#Support = supported by at least 50 customers: 50/40822[1] = .001
Bookbaskets_rules_50 <- apriori(bookbaskets, parameter = list(support = 0.001, confidence = 0.75))
Bookbaskets_rules_50 <- apriori(bookbaskets, parameter = list(support = 0.001, confidence = 0.80))

#Outcome = 101 rules
#c .80 = 84 rules

summary(Bookbaskets_rules_50)
```
```{r}
# Inspect rules
summary(Bookbaskets_rules_50)
print(Bookbaskets_rules_50)
inspect(Bookbaskets_rules_50)
```
```{r}
# Trying to identify actionable non-trivial rules
# I'll sort by lift and look at the top 10 rules and see if anything stands out
newrule <- inspect(sort(Bookbaskets_rules_50, decreasing = TRUE,by="confidence"))







```

```{r}
# Trying to identify actionable non-trivial rules
# I'll sort by lift and look at the next set


```
```{r}
# Stephanie Plum appears to be a popular author - Let's see how many rules include Stephanie Plum

stephaniePlum_rules <- subset(newrule,items%pin%"Stephanie Plum")

```
```{r}

inspect(stephaniePlum_rules)
#Google search show Stephanie Plum isn't the author but character in a book series

inspect(newrule)


```
#*****************************************************************************************************************************************************************
# A vast majority of the sets indicate that customers  tend to buy multiple titles within the same series.
# While it is understood that books of the sames series should be displayed together.
#My recommendations is to place the first book of the popular series in a display case at the end of the aisle.
# Since the series titles are displayed together by default, We should target those customers finishing up on one series
# Our display case becomes a list of suggested series. Based on lift of these sets I don't see customers moving from series to series. 
# Our display case should include the title from the Harry Potter series, Stephanie Plum series, Left Behind series, Key of Valor & The Queen of the Damned titles could also be included.
#*****************************************************************************************************************************************************************
 










